### 2023-10-29 Proposal.tex
This commit is for pdf formationt

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Proposal: Data analytics effects in major league baseball}
\author{Chenyu Mu\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}

\maketitle

\paragraph{Introduction}
Baseball, spanning from the Civil War era to the Civil Rights movement and continuing through various historical epochs,
serves as a mirror reflecting numerous facets of American life. This beloved sport is deeply intertwined with the nation's culture,
economics, and technological progress. It has the power to catalyze movements, nurture a sense of pride, and even contribute to the healing of cities.
The objective of this study aimed to assess the effectiveness of sports psychology. Baseball was selected as the focal sport due to its comprehensive nature,
allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. Previous studies 
in the field \citep[e.g.,][]{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.

\paragraph{Specific Aims}
We measure performance in these two dimensions: (1) the player's subjective assessment of their performance. 
(2) the statistical analysis of the player's actual performance. Consequently, the research inquiries encompass the following:
Does sports psychology have an effect on a player's physical performance?
Does sports psychology have an effect on the way a player feels about his performance?
Can sports psychology be used to ensure that a player is almost always giving his best performance?

\paragraph{Data}
The data is from UConn baseball 2023. Following are definitions we may use:
**AB** at bats 
**AVG**batting average 
**BB**bases on balls 
**ER**earned runs
**H**hits; holds
**K**killed 
**OBP**on base percentage

\paragraph{Research Design and Methods}
The study was designed as a two-sample experiment employing a differences-in-differences analysis approach.
Participants were categorized into three positional groups and further divided into either control or experimental groups. 
These results were evaluated as t-tests for differences in mean between groups.Method way\citep[e.g.,][]{Dalmass2018baseball}.

\paragraph{Discussion}
These limitations encompassed various factors, including but not restricted to the sample size, the participants' in-season playing time,
and the number of at-bats and innings pitched. The relatively small sample size utilized in the study, which significantly impacted the practicality of the results.

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

\end{document}

### 2023-10-30 manuscription/manuscription.tex
Try

--- 2023-10-29 Proposal.tex
@@
 
-\title{Proposal: Data analytics effects in major league baseball}
+\title{Data analytics effects in Baseball}
 \author{Chenyu Mu\\
@@
 
-\paragraph{Introduction}
-Baseball, spanning from the Civil War era to the Civil Rights movement and continuing through various historical epochs,
-serves as a mirror reflecting numerous facets of American life. This beloved sport is deeply intertwined with the nation's culture,
-economics, and technological progress. It has the power to catalyze movements, nurture a sense of pride, and even contribute to the healing of cities.
-The objective of this study aimed to assess the effectiveness of sports psychology. Baseball was selected as the focal sport due to its comprehensive nature,
-allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. Previous studies 
-in the field \citep[e.g.,][]{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
+\begin{abstract}
+  Over the past two decades, there has been a notable resurgence in the utilization of data analytics across professional sports, businesses, and governmental sectors.
+  This article will delve into an in-depth analysis of the myriad factors that potentially impact baseball players while they are actively engaged in the game. 
+  The study aims to explore and elucidate the diverse elements that might influence and shape the performance, strategies, and outcomes within the realm of baseball. 
+  \end{abstract}
+
+\section{Introduction}
+\label{sec:intro}
+Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
+Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
+Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
+Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field.
+Previous studies in the field \citet*{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
 
@@
 
-\paragraph{Data}
+\section{Data}
+\label{sec:data}
 The data is from UConn baseball 2023. Following are definitions we may use:
@@
 
-\paragraph{Research Design and Methods}
+\section{Methods}
+\label{sec:meth}
 The study was designed as a two-sample experiment employing a differences-in-differences analysis approach.
@@
 
-\paragraph{Discussion}
+\section{Results}
+\label{sec:resu}
 These limitations encompassed various factors, including but not restricted to the sample size, the participants' in-season playing time,

### 2023-10-30 manuscription/manuscription.tex
Introduction and Abstract completed

@@
 %% meta data
-
 \title{Data analytics effects in Baseball}
@@
 Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field.
-Previous studies in the field \citet*{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
+Previous studies in the field \citet{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
 
-\paragraph{Specific Aims}
-We measure performance in these two dimensions: (1) the player's subjective assessment of their performance. 
-(2) the statistical analysis of the player's actual performance. Consequently, the research inquiries encompass the following:
-Does sports psychology have an effect on a player's physical performance?
-Does sports psychology have an effect on the way a player feels about his performance?
-Can sports psychology be used to ensure that a player is almost always giving his best performance?
+We measure performance in these two dimensions: 
+\begin{enumerate}
+\item the player's subjective assessment of their performance. 
+\item the statistical analysis of the player's actual performance. Consequently, the research inquiries encompass the following:
+\end{enumerate}
+\begin{itemize}
+  \item Does sports psychology have an effect on a player's physical performance?
+  \item Does sports psychology have an effect on the way a player feels about his performance?
+  \item Can sports psychology be used to ensure that a player is almost always giving his best performance?
+\end{itemize}
+
+% roadmap
+The rest of the paper is organized as follows.
+The data will be presented in Section~\ref{sec:data}.
+The methods are described in Section~\ref{sec:meth}.
+The results are reported in Section~\ref{sec:resu}.
+A discussion concludes in Section~\ref{sec:disc}.
 
@@
 \label{sec:data}
-The data is from UConn baseball 2023. Following are definitions we may use:
-**AB** at bats 
-**AVG**batting average 
-**BB**bases on balls 
-**ER**earned runs
-**H**hits; holds
-**K**killed 
-**OBP**on base percentage
+Following are definitions we may use:\\
+$AB$: At bats\\ 
+$AVG$: Batting average\\ 
+$H$: Hits\\
+$K$: Killed,Strikeout \\
+$HR$: Home Run\\
+$BABIP$: Batting Average on Balls in Play\\
+$SF$: sacrifice flies\\
+\begin{equation}
+  \label{eq:AVG}
+  AVG = H/AB,
+\end{equation}
+which means the total number of hits divided by the total number of at-bats
+\begin{equation}
+  \label{eq:BABIP}
+  BABIP = (H - HR) / (AB - K - HR - SF),
+\end{equation}
+which states that a batter's average for balls that are put in play (excludes strikeouts, home runs, and sacrifice flies)
 
@@
 
+\section{Discussion}
+\label{sec:disc}
+
 \bibliography{../manuscript/refs}

### 2023-10-30 manuscription/manuscription.tex
method, result sections change

@@
 Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field.
-Previous studies in the field \citet{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
+Previous studies in the field \cite{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
 
@@
 % roadmap
-The rest of the paper is organized as follows.
-The data will be presented in Section~\ref{sec:data}.
-The methods are described in Section~\ref{sec:meth}.
-The results are reported in Section~\ref{sec:resu}.
-A discussion concludes in Section~\ref{sec:disc}.
+The rest of the paper is organized as follows.\\
+The data will be presented in Section~\ref{sec:data}.\\
+The methods are described in Section~\ref{sec:meth}.\\
+The results are reported in Section~\ref{sec:resu}.\\
+A discussion concludes in Section~\ref{sec:disc}.\\
 
@@
 
+We can see the number of players in each team in Figure~\ref{fig:team}.
+\graphicspath{{images/}}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{baseball team.pdf}
+  \caption{The number of players in each team in 2016 batting dataset}
+  \label{fig:team}
+\end{figure}
+
 \section{Methods}
 \label{sec:meth}
-The study was designed as a two-sample experiment employing a differences-in-differences analysis approach.
-Participants were categorized into three positional groups and further divided into either control or experimental groups. 
-These results were evaluated as t-tests for differences in mean between groups.Method way\citep[e.g.,][]{Dalmass2018baseball}.
+The research was structured as a two-sample experiment utilizing a differences-in-differences analysis method.
+The participants were classified into three positional groups and then subdivided into either control or experimental groups. 
+The outcomes were assessed using t-tests to analyze the differences in means between the groups.Method way\cite*{Dalmass2018baseball}.
 
@@
 
+\begin{table}[tbp]
+  \caption{The distribution of censored participants}
+  \label{tab:rv}
+\centering
+\begin{tabular}{rrrr}
+  \toprule
+  Position & Assigned Group & Did Not Meet AB or IP & Did Not Play\\ 
+  \midrule
+Pitcher & Control & 3 & 1\\
+Pitcher & Experiment & 2 & 1\\
+Infield & Control & 1 & 0 \\
+Infield & Experiment & 2 & 2\\
+Outfield & Control & 1 & 0\\
+Outfield & Experiment & 1 & 0\\
+  \bottomrule
+\end{tabular}
+\end{table}
+
 \section{Discussion}
@@
 
-\bibliography{../manuscript/refs}
+\begin{thebibliography}{9}
+
+  \bibliography{refs.bib}
   \bibliographystyle{chicago}
+\end{thebibliography}
 

### 2023-10-30 manuscription/manuscription.tex
draft1

@@
 Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field.
-Previous studies in the field \cite{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
+Previous studies in the field \cite*{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
 
@@
 The results are reported in Section~\ref{sec:resu}.\\
-A discussion concludes in Section~\ref{sec:disc}.\\
 
@@
 
-\section{Discussion}
-\label{sec:disc}
+The study involved recruiting 26 members from the baseball team. Among these participants, 0.385, were pitchers, 0.423 were infielders, and 0.192 were outfielders. 
+Splitting these groups, half of the pitchers were in the control group, while the remaining half were in the experimental group. For the infielders, 
+0.455 were in the control group, and 0.545 were in the experimental group. As for the outfielders, 0.4 were in the control group, and 0.6 were in the experimental group.
+Due to limitations in the sample size—considered small—the study's reliability may have been affected since it was conducted as a convenience sample. 
+While the recruitment method was straightforward as it targeted the university's varsity team, the size of the sample could potentially impact the study's outcomes. 
+Notably, the study would have ideally required a minimum sample size of 128, calculated using a specific formula considering an alpha level of .05, t-tests for independent groups, 
+an effect size of 0.5, and a power of 0.8. Implementing this study on a larger scale, such as within a Minor League Baseball organization, 
+would have made achieving the required sample size more feasible.
 
-\begin{thebibliography}{9}
-
-  \bibliography{refs.bib}
-  \bibliographystyle{chicago}
-\end{thebibliography}
+\bibliographystyle{chicago} % We choose the "plain" reference style
+\bibliography{refs} % Entries are in the refs.bib file
 

### 2023-12-04 manuscription/manuscription.tex
draft1
Improved introduction section content

@@
 \usepackage{natbib}
-% highlighting hyper links
+\usepackage{url}
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
@@
 %% meta data
-\title{Data analytics effects in Baseball}
+\title{Data analytics effects in Baseball player's value}
 \author{Chenyu Mu\\
@@
 \begin{abstract}
-  Over the past two decades, there has been a notable resurgence in the utilization of data analytics across professional sports, businesses, and governmental sectors.
-  This article will delve into an in-depth analysis of the myriad factors that potentially impact baseball players while they are actively engaged in the game. 
-  The study aims to explore and elucidate the diverse elements that might influence and shape the performance, strategies, and outcomes within the realm of baseball. 
+  Over the past two decades, there has been a notable resurgence in the utilization of data analytics across 
+  professional sports, businesses, and governmental sectors. We can measure the value of baseball players through
+  data analysis, which is very important to the success of the team. Therefore, this article will study how to 
+  measure the value of a player and will delve into an in-depth analysis of the myriad factors that potentially 
+  impact baseball players while they are actively engaged in the game. 
 \end{abstract}
@@
 \label{sec:intro}
-Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
-Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
-Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
-Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field.
-Previous studies in the field \cite*{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.
 
-We measure performance in these two dimensions: 
+The surge in the availability of data, from player statistics to in-game metrics, has ushered in a new era in 
+baseball analysis. This wealth of information has not only enriched the fan experience but has also become an 
+invaluable tool for teams and analysts seeking a competitive edge. So how do we measure the value of players in
+a statistical way?Before discussing how to measure value, we need to discuss the definition of value. 
+According to the definition in Wyers' article "How to measure a player's value"\cite*{web:Wyers:Part1}, we define 
+the value of a player as "A player's value is his contributions to his team based upon his on-field performance 
+(hitting, running, fielding and pitching) in a neutral context.This definition excludes qualities like leadership 
+and character, which would be horrific to see a statistical measure of performance attempt to portray! That's not 
+to argue these things don't matter; they just aren't easily quantified. In addition, according to Wyers' approach, 
+we need to emphasize that this is a neutral environment. First, we want to quantify a player's performance apart 
+from his teammates' - a player is no better or worse on a good or terrible team. Besides, we aim to separate a 
+player from his surroundings. A terrible pitcher does not become a better pitcher by pitching in Petco Park, and 
+a poor hitter does not become a better pitcher by hitting in Coors Field.\\
+
+We should realize there are some limits may effects our statistical model:
 \begin{enumerate}
-\item the player's subjective assessment of their performance. 
-\item the statistical analysis of the player's actual performance. Consequently, the research inquiries encompass the following:
+\item The data itself. Errors can occur, including transcription errors and similar inaccuracies. Additionally, 
+certain determinations rely on borderline judgments, such as discerning whether an event constitutes a hit or an
+error, categorizing a hit as a fly ball or a line drive, and determining whether a pitch is a ball or a strike.
+
+\item Critical information might be omitted from the data, necessitating inference or deliberate oversight. 
+Questions such as the shortstop's positioning on the field or whether the coach executed a hit-and-run strategy may 
+not be explicitly recorded and might require additional interpretation or intentional exclusion.
+
+\item Developing a model without a grasp of the fundamental principles poses challenges. The inherent value
+difference between a double and a sacrifice fly in baseball may be intuitive, but expressing and capturing this 
+nuanced understanding can be particularly challenging for a linear regression model.
+
+\item The model overlooks certain factors, such as the quality of the opponent, platoon advantage, and other 
+relevant considerations.
+
+\item Neglecting to consider subtle distinctions between players, such as the influence of a ballpark on the home 
+run rates of individuals like Barry Bonds and Juan Pierre, can lead to oversights in the analysis.
 \end{enumerate}
-\begin{itemize}
-  \item Does sports psychology have an effect on a player's physical performance?
-  \item Does sports psychology have an effect on the way a player feels about his performance?
-  \item Can sports psychology be used to ensure that a player is almost always giving his best performance?
-\end{itemize}
+
+在添加一些部分在这
+
+\cite*{web:Wyers:Part2}
 
 % roadmap
-The rest of the paper is organized as follows.\\
-The data will be presented in Section~\ref{sec:data}.\\
-The methods are described in Section~\ref{sec:meth}.\\
-The results are reported in Section~\ref{sec:resu}.\\
+The rest of the paper is organized as follows.
+
+The data will be presented in Section~\ref{sec:data}.
+
+The methods are described in Section~\ref{sec:meth}.
+
+The results are reported in Section~\ref{sec:resu}.
 
@@
 \label{sec:meth}
-The research was structured as a two-sample experiment utilizing a differences-in-differences analysis method.
-The participants were classified into three positional groups and then subdivided into either control or experimental groups. 
-The outcomes were assessed using t-tests to analyze the differences in means between the groups.Method way\cite*{Dalmass2018baseball}.
+We will use UConn baseball team data for our research and use Wyers's method \citet*{web:Wyers:Part2} that "
+A player's value is essentially an average team's runs or wins with that player, minus their runs or wins without 
+that player."
 
@@
 These limitations encompassed various factors, including but not restricted to the sample size, the participants' in-season playing time,
-and the number of at-bats and innings pitched. The relatively small sample size utilized in the study, which significantly impacted the practicality of the results.
+and the number of at-bats and innings pitched. The relatively small sample size utilized in the study, which significantly impacted the practicality of the results Table~\ref{tab:rv}.
 
@@
 
-\bibliographystyle{chicago} % We choose the "plain" reference style
-\bibliography{refs} % Entries are in the refs.bib file
+\bibliographystyle{plain}
+\bibliography{refs}
 

### 2023-12-16 manuscription/manuscription.tex
Improved introdcution section.
Improving method section, result section and discussion

@@
 \documentclass[12pt]{article}
+\usepackage{setspace}
+\doublespacing
+
+%% preamble: Keep it clean; only include those you need
 \usepackage{amsmath}
@@
 \usepackage{natbib}
-\usepackage{url}
+
+% highlighting hyper links
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
@@
 
-在添加一些部分在这
-
-\cite*{web:Wyers:Part2}
+Every value indicator has an underlying baseline, whether by chance or design. As a result, it is advisable to 
+carefully analyze the choice of a baseline and the reasoning behind it. Baselines are important since we are not 
+interested in a single player - there is no such thing as a baseball player in isolation. We're interested in a 
+player's contributions in the context of a team - the marginal contribution of that player in comparison to who 
+else could have played instead. If you've ever spent a lot of time on baseball forums or message boards, you've 
+probably seen an idea that starts with, "What could it hurt to do this?" It's the opportunity cost: playing time 
+is a fixed commodity that cannot be transferred from one player to another. Now let's start to talk about the
+detail process of value baseball players.
 
@@
 
+A discussion concludes in Section~\ref{sec:disc}.
+
 \section{Data}
 \label{sec:data}
-Following are definitions we may use:\\
-$AB$: At bats\\ 
-$AVG$: Batting average\\ 
-$H$: Hits\\
-$K$: Killed,Strikeout \\
-$HR$: Home Run\\
-$BABIP$: Batting Average on Balls in Play\\
-$SF$: sacrifice flies\\
+
+We got the 2008 season stats for 30 teams from Fangraphs website, including team name, plate appearence, average, 
+pitches and so on. We then process the data we collect using the code mentioned in Figure~ \ref*{fig:baseballcode}.The 
+data \ref{tab:PF_PFPA} and all player data is drawn from the Stats section of Fangraphs \cite*{web:data}.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{baseballcode.pdf}
+  \caption{code for addressing stats 2008 baseball team}
+  \label{fig:baseballcode}
+\end{figure}
+
+\section{Methods}
+\label{sec:meth}
+
+As Wyers mentioned  "A player's value is essentially an average team's 
+runs or wins with that player, minus their runs or wins without that player." \citep*{web:Wyers:Part2} We have two 
+types of models: dynamic and linear. Dynamic models excel in assessing entire contexts, such as a team's overall performance or 
+a pitcher's effectiveness. However, they are less effective when applied to individual hitters, as each hitter 
+only influences a fraction of the overall context. Additionally, a hitter's performance 
+does not interact with itself; for instance, if a hitter walks, they cannot subsequently hit a home run to drive 
+themselves in.
+
+On the other hand, linear models are adept at capturing the environmental context, making them 
+well-suited for estimating a hitter's contribution to a specific context. However, they may not perform as 
+effectively when evaluating pitchers.
+
+Among dynamic run estimators, BaseRuns stands out as the most accurate and versatile. The formula for BaseRuns is:
+
+\begin{equation}
+  \label{eq:baseRuns}
+A*B/(B + C) + D
+\end{equation}
+
+Where $A$ is the number of baserunners, $B$ is the “advancement factor,” $C$ is the number of outs, and $D$ is the 
+number of home runs.
+
+There are nearly too many linear weights formulas to name when it comes to linear run estimators. It's generally 
+ideal to utilize bespoke linear weights dependent on the season for a player value system. The most important 
+factor to consider is baseline—while all dynamic run estimators provide absolute runs, certain linear run estimators
+provide runs above average instead.
+
+Following are definitions we may use:
+\begin{table}[htbp]
+  \caption{Baseball Batting Statistics}
+  \label{tab:discription} 
+  \centering
+  \begin{tabular}{|l|l|}
+     \hline
+     \textbf{Variable} & \textbf{Description}\\
+     \hline
+     $AB$ & At bats\\
+     $AVG$ & Batting average\\
+     $H$ & Hits\\
+     $K$ & Strikeouts\\
+     $HR$ & Home Run\\
+     $BABIP$ & Batting Average on Balls in Play\\
+     $SF$ & Sacrifice flies\\
+    \hline
+  \end{tabular}
+\end{table}
+
 \begin{equation}
@@
 \end{equation}
-which states that a batter's average for balls that are put in play (excludes strikeouts, home runs, and sacrifice flies)
-
-We can see the number of players in each team in Figure~\ref{fig:team}.
-\graphicspath{{images/}}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{baseball team.pdf}
-  \caption{The number of players in each team in 2016 batting dataset}
-  \label{fig:team}
-\end{figure}
-
-\section{Methods}
-\label{sec:meth}
-We will use UConn baseball team data for our research and use Wyers's method \citet*{web:Wyers:Part2} that "
-A player's value is essentially an average team's runs or wins with that player, minus their runs or wins without 
-that player."
+which states that a batter's average for balls that are put in play (excludes strikeouts, home runs, and 
+sacrifice flies)
 
@@
 \label{sec:resu}
-These limitations encompassed various factors, including but not restricted to the sample size, the participants' in-season playing time,
-and the number of at-bats and innings pitched. The relatively small sample size utilized in the study, which significantly impacted the practicality of the results Table~\ref{tab:rv}.
+In assessing a player's offensive value, a linear system proves to be most effective. Linear systems
+provide insights into the number of runs a player adds to an average team. It's important 
+to note that linear weights values may not necessarily sum up to team totals accurately, 
+particularly for teams that excel or struggle significantly on the offensive front. If we're going to use a 
+linear run estimator, shouldn't we also use a linear park factor? We simply 
+take the average number of runs per plate appearance—roughly.122 in 2008—and park compensate for the 
+difference. Simply multiply that figure by the number of plate appearances and add it to the 
+linear weight values to get your park adjustment. And that is all there is to it. Simply put, 
+you have a measure of a player's offensive worth relative to the average.
+This gives us a linear factor to work with, as shown Table~ \ref*{tab:PF_PFPA}
 
-\begin{table}[tbp]
-  \caption{The distribution of censored participants}
-  \label{tab:rv}
+\begin{table}[ht]
+  \caption{Park value formula and its per plate appearance in each team}
+  \label{tab:PF_PFPA} 
   \centering
-\begin{tabular}{rrrr}
-  \toprule
-  Position & Assigned Group & Did Not Meet AB or IP & Did Not Play\\ 
-  \midrule
-Pitcher & Control & 3 & 1\\
-Pitcher & Experiment & 2 & 1\\
-Infield & Control & 1 & 0 \\
-Infield & Experiment & 2 & 2\\
-Outfield & Control & 1 & 0\\
-Outfield & Experiment & 1 & 0\\
-  \bottomrule
+  \resizebox{\columnwidth}{!}{
+    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+      \hline
+      TEAM & PF & PFPA & TEAM & PF & PFPA & TEAM & PF & PFPA\\ 
+      \hline
+     ARI & 1.05 & 0.006 & ATL & 1.00 & 0.000 & BAL & 1.01 & 0.001\\
+     BOS & 1.04 & 0.005 & CHA & 1.04 & 0.005 & CHN & 1.04 & 0.005\\
+     CIN & 1.02 & 0.002 & CLE & 1.00 & 0.000 & COL & 1.09 & 0.011\\
+     DET & 1.00 & 0.000 & FLA & 0.98 & -0.002 & HOU & 0.99 & -0.001\\
+     KC & 1.00 & 0.000 & LAA & 0.98 & -0.002 & LAN & 0.99 & -0.001\\
+     MIL & 1.00 & 0.000 & MIN & 1.00 & 0.000 & NYA & 1.00 & 0.000\\
+     NYN & 0.97 & -0.004 & OAK & 0.98 & -0.002 & PHI & 1.02 & 0.002\\
+     PIT & 0.98 & -0.002 & SD & 0.92 & -0.010 &SEA & 0.97 & -0.004 \\
+     SF & 1.01 & 0.001 & STL & 0.98 & -0.002 &TB & 0.99 & -0.001\\
+     TEX & 1.03 & 0.004 & TOR & 1.02 & 0.002 & WAS & 1.01 & 0.001\\
+
+    \end{tabular}
+  }
+  \cite*{web:Wyers:Part3}
+\end{table}
+
+Now we should consider defense value of a player. Begin using the Revised Zone Rating statistics \citep*{web:Studeman2007Field} 
+available on THT (Figure~\ref*{fig:baseballcode}). We have a metric for playing time 
+(BIZ, or balls in zone) and plays made (Plays and OOZ, or out of zone plays). What we want to 
+do is compare these to the average, convert the plays to runs, and then correct for position differences.
+\begin{equation}
+  \label{eq:RZR}
+  BIZ * (PlayerRZR - LeagueRZR) + Innings * (PlayerOOZ/PlayerInn - LeagueOOZ/LeagueInn)
+\end{equation}
+
+Subsequently, converting plays to runs involves a straightforward application of a constant. The adjustment
+for position is then made by distributing the variance between positions proportionally according to playing 
+time. This positional adjustment should be determined by assessing the relative defensive difficulty among 
+positions, a measurement attainable by examining players who occupy multiple positions. Table~\ref*{tab:def_metrics}
+is the comprehensive breakdown.
+
+\begin{table}[htp]
+  \caption{Full Nitty-Gritty}
+  \label{tab:def_metrics} 
+  \centering
+  \resizebox{\columnwidth}{!}{
+    \begin{tabular}{|l|c|c|c|c|c|c|}
+     \hline
+      Position & RZR (Revised Zone Rating) & OOZ\_INN (Out of Zone Plays per Inning) & Run/Play & BIZ/30 (Balls in Zone per 30 Innings) & PAdj (Positional Adjustment)\\
+     \hline
+     1B & 0.739422 & 0.030305 & 0.798 & 219 & -12.5\\
+     2B & 0.821831 & 0.026007 & 0.754 & 426 & 2.5\\
+     3B & 0.696536 & 0.038408 & 0.8 & 354.1333 & 2.5\\
+     CF & 0.921688 & 0.067393 & 0.842 & 349.0333 & 2.5\\
+     LF & 0.882837 & 0.04453 & 0.831 & 275.4 & -7.5\\
+     RF & 0.899098 & 0.048531 & 0.843 & 292.0333 & -7.5\\
+     SS & 0.828403 & 0.037678 & 0.753 & 424.8333 & 7.5\\
+    \end{tabular}
+  }
+\cite*{web:Wyers:Part3}
+\end{table}
+
+The top 10 position players, 2008
+
+\begin{table}[htbp]
+  \caption{Top 10 Player in 2008}
+  \label{tab:top} 
+  \centering
+  \begin{tabular}{|l|l|c|c|c|c|c|}
+     \hline
+     \textbf{Last Name} & \textbf{First Name} & \textbf{Offesne} & \textbf{Bonus} & \textbf{Defense} & \textbf{Total} & \textbf{WAR}\\
+     \hline
+     Pujols & Albert & 73.3 & 18.3 & 16.7 & 108.4 & 10.8\\
+     Jones & Chipper & 51.5 & 15.3 & 18.1 & 84.9 & 8.5\\
+     Utley & Chase & 33.6 & 20.2 & 30.0 & 83.7 & 8.4\\
+     Berkman & Lance & 49.5 & 19.0 & 12.6 & 81.0 & 8.1\\
+     Rodriguez & Alex & 39.0 & 21.2 & 14.3 & 74.4 & 7.4\\
+     Teixeira & Mark & 45.5 & 21.2 & 7.2 & 74.0 & 7.4\\
+     Ramirez & Hanley & 40.8 & 19.8 & 9.6 & 70.2 & 7.0\\
+     Wright & David A & 41.0 & 21.0 & 7.3 & 69.4 & 6.9\\
+     Beltran & Carlos & 30.4 & 20.2 & 16.8 & 67.4 & 6.7\\
+     Sizemore & Grady & 30.1 & 26.6 & 8.1 & 64.8 & 6.5\\
+    \hline
   \end{tabular}
@@
 
-The study involved recruiting 26 members from the baseball team. Among these participants, 0.385, were pitchers, 0.423 were infielders, and 0.192 were outfielders. 
-Splitting these groups, half of the pitchers were in the control group, while the remaining half were in the experimental group. For the infielders, 
-0.455 were in the control group, and 0.545 were in the experimental group. As for the outfielders, 0.4 were in the control group, and 0.6 were in the experimental group.
-Due to limitations in the sample size—considered small—the study's reliability may have been affected since it was conducted as a convenience sample. 
-While the recruitment method was straightforward as it targeted the university's varsity team, the size of the sample could potentially impact the study's outcomes. 
-Notably, the study would have ideally required a minimum sample size of 128, calculated using a specific formula considering an alpha level of .05, t-tests for independent groups, 
-an effect size of 0.5, and a power of 0.8. Implementing this study on a larger scale, such as within a Minor League Baseball organization, 
-would have made achieving the required sample size more feasible.
+The buttom 10 position players, 2008
+\begin{table}[htbp]
+  \caption{Buttom 10 Players in 2008}
+  \label{tab:buttom} 
+  \centering
+  \begin{tabular}{|l|l|c|c|c|c|c|}
+     \hline
+     \textbf{Last Name} & \textbf{First Name} & \textbf{Offense} & \textbf{RepBonus} & \textbf{Defense} & \textbf{Total} & \textbf{WAR}\\
+     \hline
+     Wilkerson & Brad & -13.9 & 11.0 & -9.4 & -12.3 & -1.2\\
+     Balentien & Wladimir R & -16.1 & 9.3 & -6.0 & -12.9 & -1.3\\
+     Jacobs & Mike & 5.4 & 14.8 & -31.5 & -11.3 & -1.1\\
+     Matthews Jr. & Gary & -12.6 & 17.0 & -16.4 & -11.9 & -1.2\\
+     Patterson & Corey & -29.4 & 11.2 & 4.7 & -13.5 & -1.4\\
+     Lamb & Mike & -15.6 & 9.6 & -8.5 & -14.4 & -1.4\\
+     Francoeur & Jeff B & -26.0 & 18.7 & -4.6 & -11.9 & -1.2\\
+     Pena & Tony F & -30.4 & 8.4 & 6.2 & -15.8 & -1.6\\
+     Guillen & Jose & -9.7 & 22.6 & -28.3 & -15.4 & -1.5\\
+     Gload & Ross & -15.4 & 14.9 & -20.1 & -20.6 & -2.1\\
+    \hline
+  \end{tabular}
+\end{table}
+
+\section{discussion}
+\label{sec:disc}
+
+These models are not flawless since no model is. We should constantly 
+strive to improve these models.At THT, we use Fielding Independent Pitching, a basic but successful 
+methodology. However,to apply linear models to pitching and thus 
+employ a dynamic FIP based on BaseRuns. In most circumstances, the distinction is likely to be trivial, 
+but for exceptionally good or awful pitchers, it will be significant.
+
+Besides, some Baseball fans can be tremendously protective of their home team's players 
+- or they can be incredibly vicious. This is heavily influenced by how good this player 
+is and how well the team has lately performed. Fans also like to believe that their long, 
+patient commitment to their ballclub has resulted in an unfathomable amount of knowledge about 
+the players they follow that is not readily available to outsiders.
+
+Analyzing player performance in baseball necessitates a holistic approach that extends beyond 
+the confines of a single season or a limited set of matches. While the data from Fangraphs in 2008 provides 
+valuable insights, it is crucial to recognize that a player's true quality is multifaceted. Factors such as mental
+acuity, strategic prowess, and long-term growth rates play pivotal roles in shaping a player's overall 
+competence in baseball.
+
+In order to comprehensively evaluate and understand a player's capabilities, it becomes imperative 
+to gather a more extensive dataset spanning multiple seasons. This broader scope allows for a nuanced 
+examination of a player's consistency, adaptability, and resilience over time. Moreover, developing more 
+sophisticated and comprehensive analytical models can enhance our ability to unravel the intricate layers of 
+a player's performance, going beyond mere statistical outputs to capture the intangible qualities that contribute
+to their success on the baseball field. By incorporating a diverse range of factors, we can build models 
+that provide a more accurate and nuanced representation of a player's true value within the sport.
 

### 2023-12-16 manuscription/manuscription.tex
Updated Method secion by adding more content should consider

@@
 
-Following are definitions we may use:
+Measuring playing time in baseball isn't always straightforward. At the team level, the fundamental unit is the
+out, crucial for both offense and defense. Pitchers and fielders often use outs, games, or innings, but when 
+it comes to batting, plate appearances or at-bats are commonly used. The challenge arises as plate appearances 
+are not fixed, impacting a player's contribution.Most run estimators focus on runs per out,
+emphasizing the importance of using the correct unit of playing 
+time. Linear run estimators typically use plate appearances. It's crucial to recognize that comparing players 
+should consider the same number of batting outs, not plate appearances.To make it more relatable, 
+some analysts convert runs per out to runs per plate appearance. This simplification 
+helps those more accustomed to plate appearances as the unit of playing time for hitters. The key is precision 
+when comparing and evaluating player performance metrics.
+
+In sabermetrics, it's widely accepted that a player's runs contribution should be separated from the 
+impact of their home park. The debate revolves around using either simple, run-based park factors or more 
+detailed component park factors.
+
+For a value metric, the general preference is for run-based park factors. This adjustment accounts 
+for the fact that the value of a run can vary based on the ballpark - for instance, a run in Coors is 
+considered less valuable than a run in Petco. While there are situations where component park factors might 
+be relevant, they don't necessarily provide a "more accurate" assessment of a player's value, especially 
+concerning explaining team wins. The choice between the two depends on the specific analysis goals and nuances.
+
+Fielding value is more difficult to quantify because, while there is only one hitter, the defense has nine 
+fielders on every play. It is quite simple to determine who made a specific play, but it is frequently 
+difficult to determine who should be liable for a ball when no play is made. Various defensive metrics attempt 
+to determine who is responsible for a ball in play. In general, the better the outcomes, the more detailed the 
+underlying dataset.
+
+Table~\ref*{tab:discription}are definitions we may use 
 \begin{table}[htbp]
